---
title: "p8105_hw3_xl2834"
author: "Xiaoyu Li"
date: "10/04/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggridges)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1
```{r}
data("instacart")
```

This dataset contains `r nrow(instacart)` rows and `r ncol(instacart)` columns. 

Observations are the level of items in orders by user. There are user / order variables -- user ID, order ID, order day, and order hour. There are also item variables -- name, aisle, department, and some numeric codes. 

#### How many aisles are there, and which aisles are the most items ordered from?

```{r}
instacart %>% 
  count(aisle) %>% 
  arrange(desc(n))
```

#### Make a plot.
Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

```{r}
instacart %>% 
  count(aisle) %>% 
  filter(n > 10000) %>% 
  mutate(aisle = factor(aisle),
         aisle = fct_reorder(aisle, n)) %>% 
  ggplot(aes(x = aisle, y = n)) + 
  geom_point() +
  theme(axis.text = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

#### Make a table
Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle) %>% 
  count(product_name) %>% 
  mutate(rank = min_rank(desc(n))) %>% 
  filter(rank <= 3) %>% 
  arrange(aisle, rank) %>% 
  knitr::kable()
```

#### Apples vs ice cream.

```{r}
instacart %>% 
	filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
	group_by(product_name, order_dow) %>% 
	summarize(mean_hour = mean(order_hour_of_day)) %>% 
	pivot_wider(
		names_from = order_dow,
		values_from = mean_hour
	)
```

## Problem 2

#### Tidy the dataset
```{r}
accel_df = read_csv(
  "./data/accel_data.csv") %>%
  janitor::clean_names() %>% 
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minute",
    names_prefix = "activity_",
    values_to = "activity_count"
    ) %>% 
  mutate(activity_count = round(activity_count, digits = 0)) %>% 
  mutate(minute = as.integer(minute),
         activity_count = as.integer(activity_count),
         ) %>% 
  mutate(day_type = case_when(
    day %in% c("Saturday", "Sunday") ~ "Weekend",
    day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday") ~ "Weekday")) %>% 
  mutate(day = ordered(day, levels = c("Monday", "Tuesday", "Wednesday", "Thursday", 
                                      "Friday","Saturday", "Sunday"))) %>% 
  arrange(week, day)
```
(day_id makes no sense when ordered by day?)


The dataset contains `r nrow(accel_df)` observations and `r ncol(accel_df)` variables. There are variables for time -- week, day id, day of the week, a variable indicating weekday/weekend, and the minute of that day. There is a variable showing activity of the person in a specific minute. 

#### Total activity for each day

```{r}
daily_activity_df = 
  accel_df %>% 
  group_by(week, day) %>% 
  summarize(
    daily_activity = sum(activity_count)
  )

```

It seems that the person's activity count is steady during weekdays throughout the 5 weeks, except for Monday in Week 1 when he was less active. The activity on weekends fluctuated throughout the 5 weeks. He was more active than usual on the Saturday of Week 1 and 2, and less active on the Saturday of Week 4 and Week 5.

#### Make a plot showing daily activities


```{r}
accel_df %>% 
  group_by(day_id) %>% 
  ggplot(aes(x = minute, y = activity_count, color = day)) +
  geom_point() +
  geom_line()
```

From the graph, we can see that the person is more active at around 10-12am, while less active at other time periods on Sundays compared to other days in the week.The person is active at Friday nights and Saturday nights.  

## Problem 3

```{r}
data("ny_noaa")
```

```{r}
weather_df = 
  mutate(ny_noaa,
         tmin = as.numeric(tmin),
         tmax = as.numeric(tmax)) %>% 
  mutate(tmin = tmin / 10,
         tmax = tmax / 10,
         prcp = prcp / 10) %>% 
  separate(date, into = c("year", "month", "day"), sep = "-" ) 


weather_df %>% 
  group_by(snow) %>% 
  count(snow)
    
```

"0" is the most observed value. why?

mutate month using names?

```{r}
  
weather_df = 
  mutate(weather_df, 
         tmin = as.numeric(tmin),
         tmax = as.numeric(tmax),
         prcp = as.numeric(prcp)
         )

weather_df %>% 
  filter(month %in% c("01", "07")) %>% 
  group_by(id, month) %>%
  summarise(mean_tmax = mean(tmax, na.rm = TRUE)) 

```
error: not a number


